Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-07-29 main.Rmd
include algo for threshold
algo for threshold updated

6. Use Steps 1-4 to compute normalized maximum distance for $\forall k \in  \{1, 2, \ldots, K\}$.

@@

>>>>

6. Use Steps 1-5 to compute normalized maximum distance for $\forall k \in  \{1, 2, \ldots, K\}$.

@@

\noindent The algorithm employed for selecting harmonies with significant variation is summarized as follows:

- **Input:** Harmony pairs $(C_i, C_j)$ $\forall i, j \in N_C$  
- **Output:** Harmony pairs $(C_i, C_j)$ for which MMPD is significant.

1. Given the measured variable; $\{v_t: t=0, 1, 2, \dots, T-1\}$, MMPD is computed for all harmony pairs and is represented by $MMPD_{obs}$.

2. From the original sequence a random permutation is obtained: $\{v_t^*: t=0, 1, 2, \dots, T-1\}$.

3. MMPD is computed for all harmony pairs for this random permutation of the data and is represented by $MMPD_{sample}$.

4.  Steps (2) and (3) are repeated a large number
of times M (e.g. 100).

5. For each permutation, one $MMPD_{sample}$ vector is obtained.

6. $95^{th}$ percentile of this $MMPD_{sample}$ distribution is computed and stored in $MMPD_{threshold}$.

7. Harmony pairs for which $MMPD_{obs}> MMPD_{threshold}$ are accepted.
